Modeling and Simulation of Load Balancing Strategies for Computing in High Energy Physics

### 2018-10-17 paper/paper.tex
Small layout changes
Use double colum for footnotes and replace github url with doi url.

\usepackage{todonotes}
\usepackage[capitalise,nameinlink]{cleveref}
%Nice formats for \cref
\crefname{section}{Sect.}{Sect.}
\Crefname{section}{Section}{Sections}
\crefname{listing}{\lstlistingname}{\lstlistingname}
\Crefname{listing}{Listing}{Listings}
\usepackage{pgfplots}

% Use package for subfigures
\usepackage{subcaption}

% layout changes
\setlength\belowcaptionskip{-15pt}
\renewcommand*{\bibfont}{\footnotesize}

@@

\author{
	\firstname{Ren\'e} \lastname{Caspart}\inst{1}\fnsep\thanks{\email{rene.caspart@cern.ch}} \and
	\firstname{Patrick} \lastname{Firnkes}\inst{2}\fnsep\thanks{\email{patrick.firnkes@student.kit.edu}} \and
	\firstname{Manuel} \lastname{Giffels}\inst{1}\fnsep\thanks{\email{manuel.giffels@cern.ch}} \and
	\firstname{Anne} \lastname{Koziolek}\inst{2}\fnsep\thanks{\email{koziolek@kit.edu}} \and
	\firstname{G\"unter} \lastname{Quast}\inst{1}\fnsep\thanks{\email{g.quast@kit.edu}} \and
	\firstname{Ralf} \lastname{Reussner}\inst{2}\fnsep\thanks{\email{reussner@kit.edu}} \and
	\firstname{Maximilian} \lastname{Stemmer-Grabow}\fnsep\thanks{\email{mail@mxsg.de}}\inst{2}
}

@@

We extended Palladio with a \textit{load balancing strategy action}\footnote{https://github.com/PalladioSimulator/Palladio-Addon-ArchitecturalTemplates-LoadBalancing}, so that we can simulate load balancing strategies.
This load balancing strategy action is contained in a load balancing component.
In the assembly model all job components are connected with the load balancing component, which is the entry point of the system.
This action decides on which node a job should be scheduled based on the currently free job slots of each working node. The load balancing strategies can be extended to evaluate different strategies.

@@

The parameter extraction tool\footnote{https://github.com/mxsg/CMS-Model-Calibration} exports model parameter sets as JSON files.
To simplify calibrating simulation models with these parameter sets, we created a Palladio plugin\footnote{https://github.com/mxsg/WLCG-Model-Construction} that can be used to automatically complete a blueprint of the simulation model (which defines the structure of the model as described in section \ref{sec:model}) with arbitrary parameter sets.
This ensures an efficient and flexible model creation process.

>>>>

\usepackage{todonotes}
\usepackage[capitalise,nameinlink]{cleveref}
%Nice formats for \cref
\crefname{section}{Sect.}{Sect.}
\Crefname{section}{Section}{Sections}
\crefname{listing}{\lstlistingname}{\lstlistingname}
\Crefname{listing}{Listing}{Listings}
\usepackage{pgfplots}
\newcommand{\footurl}[1]{\footnote{\url{#1}}}
% Use package for subfigures
\usepackage{subcaption}

% layout changes
\usepackage{dblfnote}
\setlength\abovecaptionskip{5pt}
\setlength\belowcaptionskip{-15pt}
\renewcommand*{\bibfont}{\footnotesize}

@@

\author{
	\firstname{Ren\'e} \lastname{Caspart}\inst{1}\fnsep\thanks{\email{rene.caspart@cern.ch}} \and
	\firstname{Patrick} \lastname{Firnkes}\inst{2}\fnsep\thanks{\email{patrick.firnkes@student.kit.edu}} \and
	\firstname{Manuel} \lastname{Giffels}\inst{1}\fnsep\thanks{\email{manuel.giffels@cern.ch}} \and
	\firstname{Anne} \lastname{Koziolek}\inst{2}\fnsep\thanks{\email{koziolek@kit.edu}} \and
	\firstname{G\"unter} \lastname{Quast}\inst{1}\fnsep\thanks{\email{g.quast@kit.edu}} \and
	\firstname{Ralf} \lastname{Reussner}\inst{2}\fnsep\thanks{\email{reussner@kit.edu}} \and
	\firstname{Maximilian} \lastname{Stemmer-Grabow}\inst{2}\fnsep\thanks{\email{mail@mxsg.de}}
}

@@

We extended Palladio with a \textit{load balancing strategy action}\footurl{https://doi.org/10.5281/zenodo.1464569}, so that we can simulate load balancing strategies.
This load balancing strategy action is contained in a load balancing component.
In the assembly model all job components are connected with the load balancing component, which is the entry point of the system.
This action decides on which node a job should be scheduled based on the currently free job slots of each working node. The load balancing strategies can be extended to evaluate different strategies.

@@

The parameter extraction tool\footurl{https://doi.org/10.5281/zenodo.1464569} exports model parameter sets as JSON files.
To simplify calibrating simulation models with these parameter sets, we created a Palladio plugin\footurl{https://doi.org/10.5281/zenodo.1464569} that can be used to automatically complete a blueprint of the simulation model (which defines the structure of the model as described in section \ref{sec:model}) with arbitrary parameter sets.
This ensures an efficient and flexible model creation process.
